An interactive environment for mapping computational structures to FPGAs

### 2016-07-06 paper/paper.tex
performed a spell check.

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{An interactive environment for mapping comutational structures to FPGAs}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

@@

\begin{abstract}
  In this paper we propose a methodology to translate computational structures to hardware.
  Computational structures express both the computation and the ordering of computations.
  These structures are expressed using datalfow graph from which hardware can be generated more direclty compared to imperative apporaches.
  As a proof of concept, SDFkit is developed.
  SDFkit is a cycle accurate simulation environment for these computational structures and has a backend to generate highliy parallel FPGA code.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Strucutre, Computations, FPGA, SDFkit
\end{IEEEkeywords}

@@

  FPGAs have an enormous potential in terms of computational power.
  However, they still remain hard to program even though a lot of work has been performed on translating imperative languages to hardware.
  By using a sequential language to descibe parallel hardware a structural mismatch emerges.
  A lot of analysis is therefore requiered to determine which computations are independant and ca therefore be performed in parallel.

  In this work-in-progress paper, we propose a more strucutral approach to computations.
  method..... math descrition to CSDF graph/ transformations to make efficient hardware then HW generation

  The cuccrent implementation: SFDkit, an interactive environment

@@

  Computational strucutres borrowed from functional porgramming languages so called higher-order functions.
  These functions are very suitable to express the strucutre in computations and therefore a good source of parallelism.
  \todo{ref to thesis Rinse}
  These computational structures are represented as a specific kind of dataflow graph, a cyclo static synchronous (CSDF) dataflow graph.
  Transformations are then applied to this graph to optimize performance.
  \todo{ref naar thesis Robert}
  During the final step, the graph is mapped to hardware by translating each node to a combinational component and repacing the edges by a FIFO.

@@

  \todo[inline]{decribe status of SDFkit}

  Figure \ref{fig:screenshot} shows a screenshot of SDFkit.
  The central widget shows a visualisation of a CSDF graph which can be simulated in a step-wise fashion using the control panel on the left.
  For debugging purposes, the data contained in each token for each simulation step is visualised in the lower widget.

@@

  In this paper we presented SDFkit, an interactive environment for designing applications using SDF graphs.
  In contrast to translating imperative programming constructs like for-loops to hardware, we use constructs to express the structure in a comptation.
  Using these computational structures, the generation of highly parallel hardware is tremendously simplyfied.
  Applications are modeled using CSDF graphs which are a cycle-accurate model for the generated hardware.
  \todo[inline]{extend conslusion a bit with current state of project}

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{An interactive environment for mapping computational structures to FPGAs}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

@@

\begin{abstract}
  In this paper we propose a methodology to translate computational structures to hardware.
  Computational structures express both the computation and the ordering of computations.
  These structures are expressed using dataflow graph from which hardware can be generated more directly compared to imperative approaches.
  As a proof of concept, SDFkit is developed.
  SDFkit is a cycle accurate simulation environment for these computational structures and has a backend to generate highly parallel FPGA code.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
  Structure, Computations, FPGA, SDFkit
\end{IEEEkeywords}

@@

  FPGAs have an enormous potential in terms of computational power.
  However, they still remain hard to program even though a lot of work has been performed on translating imperative languages to hardware.
  By using a sequential language to describe parallel hardware a structural mismatch emerges.
  A lot of analysis is therefore required to determine which computations are independent and ca therefore be performed in parallel.

  In this work-in-progress paper, we propose a more structural approach to computations.
  method..... math description to CSDF graph/ transformations to make efficient hardware then HW generation

  The current implementation: SDFkit, an interactive environment...

  Describe what is presented in remainder of paper..

@@

  Computational structures borrowed from functional programming languages so called higher-order functions.
  These functions are very suitable to express the structure in computations and therefore a good source of parallelism.
  \todo{ref to thesis Rinse}
  These computational structures are represented as a specific kind of dataflow graph, a cyclo static synchronous (CSDF) dataflow graph.
  Transformations are then applied to this graph to optimize performance.
  \todo{ref naar thesis Robert}
  During the final step, the graph is mapped to hardware by translating each node to a combinational component and replacing the edges by a FIFO.

@@

  \todo[inline]{describe status of SDFkit}

  Figure \ref{fig:screenshot} shows a screenshot of SDFkit.
  The central widget shows a visualization of a CSDF graph which can be simulated in a step-wise fashion using the control panel on the left.
  For debugging purposes, the data contained in each token for each simulation step is visualized in the lower widget.

@@

  In this paper we presented SDFkit, an interactive environment for designing applications using SDF graphs.
  In contrast to translating imperative programming constructs like for-loops to hardware, we use constructs to express the structure in a computation.
  Using these computational structures, the generation of highly parallel hardware is tremendously simplified.
  Applications are modeled using CSDF graphs which are a cycle-accurate model for the generated hardware.
  \todo[inline]{extend conclusion a bit with current state of project}
